Methodology for Assessing the State of the Practice for Domain X

### 2020-06-11 StateOfPractice/Methodology/Methodology.tex
updated selection criteria

%\subsection{Empirical Measures}
% \begin {enumerate}
% \item Qualitative/Quantitative
% \item Pairwise Comparison methodology needs to be described
% \item Measure time to complete a task and compare actual with expected time of completion
% \item From a list of given tasks, measure how many tasks were completed correctly
% \item Learnability
% \item Efficiency
% \item Memorability
% \item Errors
% \item Satisfaction
% \item Heuristic evaluation: Experts go through the interface to identify elements that violate usability heuristics.Popular because of its low cost and low time commitment
%\end {enumerate}

@@

\subsection{Task selection criteria}
Below are the criteria to be used in defining usability experiment tasks. The task selection will be determined with the aid of the domain expert attached to any of the selected projects. The domain expert will be asked to consider the below criteria when helping us to determine a task.
\begin {enumerate}
\item All tasks should take no more than 2 hours (in one sitting) for completion.
\item Common and popular tasks that users would perform (these apply to all selected projects collectively) with the software application.
%\item Task that would generate errors messages or error codes
%\item Tasks to check standards and conventions
%\item Tasks that provide users with the system's current state and what actions can be done or where to go or what change was made
\item Tasks related to what users will do in the real world
\item End to end tasks that require users to go through sequential or hierarchical steps.
%\item Tasks that allow users to reuse a previously defined value without having to memorize or jot it.
%\item Tasks that provide users with feedback.
%\item Tasks that allow users to customize and use shortcuts, bookmarks, command keys etc.
%\item Tasks to verify if the system is capable of preventing and /or reversing errors
%\item Tasks that would lead the user to use help or documentation
\end {enumerate}

**Domain experts will be asked to identify what background knowledge is necessary for the suggested tasks (Expert, Intermediate, Novice).

>>>>

@@

\subsection{Task selection criteria}
**The task selection will be determined with the aid of the domain expert attached to any of the selected projects.\\ 
**The domain expert will be asked to consider the below criteria when defining a task. \\
**Domain experts will also be asked to identify what background knowledge is necessary for the suggested tasks - Novice, Intermediate, Advanced
\begin {enumerate}
\item Collectively all tasks should not take no more than 2 hours.
\item Selected tasks should reflect common use cases of  the software
\item Include tasks that require a set of sequential or hierarchical steps to be completed

\end {enumerate} 
\oo   {Are domain experts expected to provide step by step instructions to complete a tasks}
